Notes for Week 2/1/18 - 2/8/18

### 2019-02-08 notes/weekly_notes/2.6.19.NotesForWeek.tex
added changes to this weeks notes

\textcolor{red}{Introduce $\bar{f}$}.

@@

\begin{enumerate}[(i)]
	\item \emph{Quantization:} Consider the function class
	\begin{equation*}
	\Wset_n = \set{\frac{\overline{f}}{\norm{Bf}_2}: f \in \Wset^{1,2}(\Dset,\rho^2)}.
	\end{equation*}
	Under assumptions,
	\begin{equation*}
	\sup_{\theta: \norm{B\theta}_2 \leq 1} \abs{\lbf^T \theta} - \sup_{\widetilde{f} \in \Wset_n} \abs{\Pbb_n \widetilde{f} - \Qbb_n \widetilde{f}} = o_{\Pbb}(n^{-1/2})
	\end{equation*}
	\item \emph{Donsker-convergence of empirical process:} Write 
	\begin{equation*}
	\widetilde{f} = \frac{\overline{f}}{\norm{Bf}_2}.
	\end{equation*}
	Under \textcolor{red}{assumptions},
	\begin{equation*}
	\set{\Gbb_{\Pbb_n}\widetilde{f}: f \in \Wset^{1,2}(\Dset,\rho^2)} \rightsquigarrow G_{\Pbb}
	\end{equation*}
	and 
	\begin{equation*}
	\set{\Gbb_{\Qbb_n}\widetilde{f}: f \in \Wset^{1,2}(\Dset,\rho^2)} \rightsquigarrow G_{\Qbb},
	\end{equation*}
	where \textcolor{red}{$G_{\Pbb}$ is a tight Gaussian process with support on $\Wset^{1,2}(\Dset,\rho^2)$} and for measures $P_n$ and $P$, $\Gbb_{P_n,P} = \sqrt{n}(P_n - P)$ and we suppress notational dependence on $P$ when obvious from context.
	\item \emph{Continuous mapping:}
	Under the null hypothesis $H_0: \Pbb = \Qbb$, for any $\widetilde{f} \in \Wset_n$, 
	\begin{equation*}
	\sqrt{n}(\Pbb_n \widetilde{f} - \Qbb_n \widetilde{f}) = (\Gbb_{\Pbb_n} - \Gbb_{\Qbb_n})\widetilde{f}
	\end{equation*}
	Thus, by i), \textcolor{red}{the independence of $\Pbb_n$ and $\Qbb_n$}, and the continuous mapping theorem,
	\begin{equation*}
	\set{\sqrt{n}(\Pbb_n \widetilde{f} - \Qbb_n \widetilde{f}), f \in \Wset^{1,2}(\Dset,\rho^2)} \rightsquigarrow G_{\Pbb} - G'_{\Pbb}
	\end{equation*}
	where $G_{\Pbb}$ and $G'_{\Pbb}$ are i.i.d. Gaussian processes.

@@

\section{Proof Strategy for ii)}

We want to exhibit a function class
\begin{equation*}
\overline{\Wset}_n = \set{f_{n,t}: t \in \Wset^{1,2}(\Dset,\rho^2)}
\end{equation*}
where $f_{n,t}: \Dset \to \Reals$ such that:  
\begin{enumerate}[(a)]
	\item 
	There exists a bijection $\phi: \Wset_n \to \overline{\Wset}_n$ with
	\begin{equation*}
	\sqrt{n}\Pbb_n(f_n - \phi(f_n)) \rightsquigarrow 0.
	\end{equation*}
	\item 
	$\overline{\Wset}_n$ is totally bounded.
	\item
	For every sequence $\delta_n \downarrow 0$,
	\begin{equation*}
	\sup_{\norm{s - t}_{1,2,\rho^2} \leq \delta_n} \Pbb(f_{n,s} - f_{n,t})^2 \to 0
	\end{equation*}
	\item
	There exists a sequence of envelope functions $F_n$ satisfying the Lindeberg condition
	\begin{align*}
	\Pbb F_n^2 & = \mathcal{O}(1) \\
	\Pbb F_n^2 \1{F_n > \epsilon \sqrt{n}} & \to 0 \tag{for any $\epsilon > 0$}
	\end{align*}
	\item The bracketing integral
	\begin{equation*}
	\int_{0}^{\delta} \sqrt{\log N_{[]}(\epsilon, \overline{W}_n, L_2(\Pbb))}
	\end{equation*}
	converges to $0$ for any $\delta_n \downarrow 0$.
\end{enumerate}

\begin{theorem}
	\label{thm: donsker_changing_classes}
	Let $\F_n = \set{f_{n,t}: t \in T}$ be a class of measurable functions indexed by a totally bounded semimetric space $(T,\rho)$ satisfying
	\begin{equation*}
	\sup_{\rho(s,t) < \delta_n} P (f_{n,s} - f_{n,t})^2 \to 0, ~~ \text{every $\delta_n \downarrow 0$}
	\end{equation*}
	and with envelope function $F_n$ satisfying the Lindeberg condition
	\begin{align*}
	PF_n^2 & = \mathcal{O}(1) \\
	PF_n^2 \1 \set{F_n > \epsilon \sqrt{n}} & \to 0, ~~ \textrm{for every $\epsilon > 0$.}
	\end{align*}
	If $J_{[]}(\delta_n, \F_n, L_2(P)) \to 0$ for every $\delta_n \downarrow 0$, then the sequence $\set{\Gbb_n f_{n,t}, t \in T}$ converges in distribution to a tight Gaussian process, provided the sequence of covariance functions
	\begin{equation*}
	P f_{n,s} f_{n,t} - P f_{n,s} P f_{n,t} 
	\end{equation*}
	converges pointwise on $T \times T$. 
\end{theorem}

>>>>

For a given function $f$, the \emph{quantization} $\bar{f}$ over $\set{C(z): z \in P_{lat}(N)}$ is defined by
\begin{equation*}
\overline{f}(x_0) = \frac{1}{\nu(C(z_0))} \int_{C(z_0)} f(x) d \nu(x)
\end{equation*}
where $x_0 \in C(z_0)$.

@@

For any function $f:\Dset \to \Reals$, let $\theta_{f}$ denote the evaluations of $f$ over $\Xbf$, meaning
\begin{equation*}
(\theta_f)_i = f(x_i)
\end{equation*}

\begin{enumerate}[(i)]
	\item \emph{Quantization:} Consider the function class
	\begin{equation}
	\label{eqn: quantized_function_class}
	\Wset_n = \set{C_{n,r}\frac{\overline{f}}{\norm{\Bbf \theta_{\bar{f}}}_2}: f \in \Wset^{1,2}(\Dset,\rho^2)}.
	\end{equation}
	Under assumptions,
	\begin{equation*}
	\sup_{\theta: \norm{B\theta}_2 \leq 1} \abs{\lbf^T \theta} - \sup_{\widetilde{f} \in \Wset_n} \abs{\Pbb_n \widetilde{f} - \Qbb_n \widetilde{f}} = o_{\Pbb}(n^{-1/2})
	\end{equation*}
	\item \emph{Donsker-convergence of empirical process:} Write 
	\begin{equation*}
	\widetilde{f} = \frac{\overline{f}}{\norm{\Bbf \theta_{\bar{f}}}_2}.
	\end{equation*}
	Under \textcolor{red}{assumptions},
	\begin{equation*}
	\set{\Gbb_{\Pbb_n}\widetilde{f}: f \in \Wset^{1,2}(\Dset,\rho^2)} \rightsquigarrow G_{\Pbb}
	\end{equation*}
	and 
	\begin{equation*}
	\set{\Gbb_{\Qbb_n}\widetilde{f}: f \in \Wset^{1,2}(\Dset,\rho^2)} \rightsquigarrow G_{\Qbb},
	\end{equation*}
	where \textcolor{red}{$G_{\Pbb}$ is a tight Gaussian process with support on $\Wset^{1,2}(\Dset,\rho^2)$} and for measures $P_n$ and $P$, $\Gbb_{P_n,P} = \sqrt{n}(P_n - P)$ and we suppress notational dependence on $P$ when obvious from context.
	\item \emph{Continuous mapping:}
	Under the null hypothesis $H_0: \Pbb = \Qbb$, for any $\widetilde{f} \in \Wset_n$, 
	\begin{equation*}
	\sqrt{n}(\Pbb_n \widetilde{f} - \Qbb_n \widetilde{f}) = (\Gbb_{\Pbb_n} - \Gbb_{\Qbb_n})\widetilde{f}
	\end{equation*}
	Thus, by i), \textcolor{red}{the independence of $\Pbb_n$ and $\Qbb_n$}, and the continuous mapping theorem,
	\begin{equation*}
	\set{\sqrt{n}(\Pbb_n \widetilde{f} - \Qbb_n \widetilde{f}), f \in \Wset^{1,2}(\Dset,\rho^2)} \rightsquigarrow G_{\Pbb} - G'_{\Pbb}
	\end{equation*}
	where $G_{\Pbb}$ and $G'_{\Pbb}$ are i.i.d. Gaussian processes.

@@

For a given $\theta \in \Reals^n$, let the quantization of $\theta$ be given by
\begin{equation*}
(\bar{\theta})_i = \frac{\sum_{x_j \in C(z_0)} \theta_j}{\abs{C(z_0)}}
\end{equation*}
where $x_i \in C(z_0)$, and $\abs{C(z_0)} = \sum_{j = 1}^{n} \1(x_j \in C(z_0))$ is the number of data points in $C(z_0)$.

\begin{lemma}
	\begin{equation*}
	\sup_{\theta: \norm{B\theta}_2 \leq C_{n,r}} \abs{\lbf^T \theta} \geq \sup_{\widetilde{f} \in \Wset_n} \abs{\Pbb_n \widetilde{f} - \Qbb_n \widetilde{f}}
	\end{equation*}
\end{lemma}
\begin{proof}
	For any $f: \Dset \to \Reals$, $\mathbb{P}_n f - \mathbb{Q}_n f = \lbf^T \theta_f$, and so
	\begin{equation*}
	\sup_{\widetilde{f} \in \Wset_n} \abs{\Pbb_n \widetilde{f} - \Qbb_n \widetilde{f}} = \sup_{\theta_{\widetilde{f}}: \widetilde{f} \in \Wset_n} \abs{\lbf^T \theta_{\widetilde{f}}}
	\end{equation*}
	Then, for $\widetilde{f} \in \Wset_n$
	\begin{equation*}
	\norm{B \theta_{\widetilde{f}}}_2 = \norm{B \theta_{\frac{C_{n,r}\overline{f}} {\norm{B \theta_{\overline{f}}}}_2}} = C_{n,r}.
	\end{equation*}
	and so $\set{\theta_{\widetilde{f}}: \widetilde{f} \in \Wset_n} \subset \set{\theta: \norm{\Bbf \theta}_2 \leq C_{n,r}}$.
\end{proof}

\begin{lemma}
	For any $\theta \in \Reals^n$
	\begin{equation*}
	\lbf^T(\theta - \overline{\theta}) \leq 2 \norm{\Bbf \theta}_{\textcolor{red}{1}}
	\end{equation*}
\end{lemma}

\begin{theorem}
	For any $\theta \in \Reals^n$ such that $\norm{\Bbf \theta}_2 \leq C_{n,r}$, there exists some $f \in \Wset^{1,2}(\Dset,\rho^2)$ such that 
	\begin{equation*}
	\abs{\Pbb_n \widetilde{f} - \Qbb_n \widetilde{f} } \geq \abs{\Pbb_n \overline{\theta} - \Qbb_n \overline{\theta} } - o_{\Pbb}(n^{-1/2})
	\end{equation*}
\end{theorem}
\begin{proof}
	For $\theta \in \Reals^n$, consider the quantized extension of $\theta$, $\overline{f}_{\theta}: \Dset \to \Reals$ defined by
	\begin{equation*}
	\overline{f}_{\theta}(x) = (\overline{\theta})_i
	\end{equation*}
	for any $x_i$ in the same cell $C(z)$ as $x$. Clearly,
	\begin{equation*}
	\Pbb_n \overline{f}_{\theta} - \Qbb_n \overline{f}_{\theta} = \Pbb_n \overline{\theta} - \Qbb_n \overline{\theta} 
	\end{equation*}
	Now, we have to show that either $\overline{f}_{\theta} \in \Wset_n$, or that it can be well-approximated by some $\widetilde{f} \in \Wset_n$. 
\end{proof}

\section{Proof strategy for \emph{Donsker-convergence of empirical processes}:}

Consider the function class $\Wset_n$ given by \eqref{eqn: quantized_function_class}. We wish to show

\begin{enumerate}[(a)]
	\item 
	$\Wset_n$ is totally bounded.
	\item
	For every sequence $\delta_n \downarrow 0$,
	\begin{equation*}
	\sup_{\norm{f - g}_{1,2,\rho^2} \leq \delta_n} \Pbb(\widetilde{f} - \widetilde{g})^2 \to 0
	\end{equation*}
	where $f$ and $g$ are arbitrary elements of $\Wset^{1,2}(\Dset,\rho^2)$.
	\item
	There exists a sequence of envelope functions $F_n$ on $\Wset_n$ satisfying the Lindeberg condition
	\begin{align*}
	\Pbb F_n^2 & = \mathcal{O}(1) \\
	\Pbb F_n^2 \1{F_n > \epsilon \sqrt{n}} & \to 0 \tag{for any $\epsilon > 0$}
	\end{align*}
	\item The bracketing integral
	\begin{equation*}
	\int_{0}^{\delta} \sqrt{\log N_{[]}(\epsilon, \Wset_n, L_2(\Pbb))}
	\end{equation*}
	converges to $0$ for any $\delta_n \downarrow 0$.
\end{enumerate}

Then, the desired results holds by application of Theorem \ref{thm: donsker_changing_classes}.

\begin{theorem}[Donsker theorem for changing function classes]
	\label{thm: donsker_changing_classes}

	Let $\F_n = \set{f_{n,t}: t \in T}$ be a class of measurable functions indexed by a totally bounded semimetric space $(T,\rho)$ satisfying
	\begin{equation*}
	\sup_{\rho(s,t) < \delta_n} P (f_{n,s} - f_{n,t})^2 \to 0, ~~ \text{every $\delta_n \downarrow 0$}
	\end{equation*}
	and with envelope function $F_n$ satisfying the Lindeberg condition
	\begin{align*}
	PF_n^2 & = \mathcal{O}(1) \\
	PF_n^2 \1 \set{F_n > \epsilon \sqrt{n}} & \to 0, ~~ \textrm{for every $\epsilon > 0$.}
	\end{align*}
	If $J_{[]}(\delta_n, \F_n, L_2(P)) \to 0$ for every $\delta_n \downarrow 0$, then the sequence $\set{\Gbb_n f_{n,t}, t \in T}$ converges in distribution to a tight Gaussian process, provided the sequence of covariance functions
	\begin{equation*}
	P f_{n,s} f_{n,t} - P f_{n,s} P f_{n,t} 
	\end{equation*}
	converges pointwise on $T \times T$. 
\end{theorem}
